On modeling for Kerr black holes: Basis learning, QNM frequencies, and spherical-spheroidal mixing coefficients

### 2019-03-28 docs/mvfits_paper/mvf.tex
Def choice of model rep err used for positive [11]
Define r distance to source [30]

\par In the first and second lines of \eqn{hrd}, we relate the observable \gw{} polarizations, $h_+$ and $h_\times$, to the analytically understood morphology of the time domain \rd{} waveform.

@@

The refinement process is to terminate when a measure of model error (e.g. the $L^2$ norm $||g^{(0)}-g^{(n)}||$) passes a predetermined threshold.

@@

@@

>>>>

\par In the first and second lines of \eqn{hrd}, we relate the observable \gw{} polarizations, $h_+$ and $h_\times$, to the analytically understood morphology of the time domain \rd{} waveform where $r$ is the distance from the source.

@@

The refinement process is to terminate when a measure of model error (e.g. the $L^2$ norm $||\vec{g}^{(0)}-\vec{g}^{(n)}||$) passes a predetermined threshold. For \cite{lionel_london_2018_1402516} the following model representation error was used

@@

  \label{eq:raterr}
  \epsilon^{(n)}  = \left|\frac{\operatorname{Var}\left(\vec{g}^{(n)} - \vec{g}^{(0)}\right)}{\operatorname{Var}\left(\vec{g}^{(0)}\right)}\right|

@@

where $\operatorname{Var}$ is the variance defined as
  \label{eq:ratvar}
  \operatorname{Var}\left(\vec{a}\right)  = \frac{1}{J}\sum_{j=0}^{J}\left(g_j - \frac{1}{J}\sum_{u=0}^{J}g_j\right)^2
